% This is paper.tex 
% Write your paper HERE.
% READ THE EXISTING PAPER BEFORE DELETING IT.
% Load TikZ libraries for shapes and positioning
\usetikzlibrary{shapes.geometric, positioning, arrows.meta}

% Define block styles using \tikzset (Modern replacement for \tikzstyle)
\tikzset{
    startstop/.style={
        draw, rectangle, rounded corners, 
        minimum width=3cm, minimum height=1cm, 
        text centered, draw=black, fill=red!20
    },
    io/.style={
        draw, trapezium, trapezium left angle=70, trapezium right angle=110, 
        minimum width=3cm, minimum height=1cm, 
        text centered, draw=black, fill=blue!20,
        trapezium stretches=true
    },
    process/.style={
        draw, rectangle, 
        minimum width=3cm, minimum height=1cm, 
        text centered, draw=black, fill=orange!20
    },
    decision/.style={
        draw, diamond, aspect=1.5,
        minimum width=3cm, minimum height=1cm, 
        text centered, draw=black, fill=green!20
    },
    arrow/.style={
        thick, ->, >=stealth
    }
}

\section{Introduction}
Short-peptide self-assembly drives critical advancements in novel biomaterials and drug delivery systems \cite{baral_assembly_2014} and is driven by a variety of factors not limited to sequence, modifications, solvent, concentration, pH, and temperature\cite{mukai_hydroorganohybrid_2013}, eventually forming a variety of nanostructures, like hydrogels, fibers, tubes, etc\cite{adler-abramovich_controlled_2008}. Additionally, self-assembly spans a long-horizon timescale, making MD simulations nearly impossible purely based on scale. As such, most data generated about short-peptide self-assembly is generated in a wet lab setting\cite{chandoliya_titanium_2024}, making it nearly impossible to centralize a knowledge base across different proteins manually. 

Thus, LLMs emerge as a promising candidate to extract and predict short-peptide self-assembly phases\cite{buehler_accelerating_2024}. The current benchmark established by Yang et al relied on a manually curated 75 paper publication set containing 1012 entries. This set maps a 13-feature schema to an 8-class morphological prediction. However, manual extraction of textual features is highly labor-intensive and extremely challenging to scale. 

While Large Language Models (LLMs) offer mechanisms for automated data extraction, direct off-the-shelf use without a handler is unreliable. Experimental conditions and results are generally sparsely distributed across methods, results, tables, and figures. So, we propose an agentic workflow that addresses this limitation by deploying knowledge graphs and highly structured processing pipelines to improve extraction accuracy, traceability, and downstream phase prediction \cite{stewart_graphagents_2026}. 
\subsection{Research Aims and Hypothesis}
The primary aim of this project is to organize unstructured short-peptide self-assembly literature into support machine learning classification. The secondary aim is to then package this automated extraction as a reusable ScienceSkill, potentially as part of a greater ScienceClaw package. 
We hypothesize that a knowledge graph-grounded, multiagent workflow yields higher extraction accuracy, traceability, and downstream phase prediction compared to direct or schema-guided Large Language Model baseline extraction methods \cite{stewart_graphagents_2026,buehler_accelerating_2024}
\section{Proposed Methdology}

\subsection{Scope}
This project operated at the knowledge extraction level, eliminating the need for manual extraction or physics-based simulations.

\begin{figure}[htb]
    \centering
    \begin{tikzpicture}[
        node distance=2cm, auto,
        startstop/.style={rectangle, rounded corners, minimum width=3.5cm, minimum height=1cm, text centered, draw=black, fill=purple!20},
        process/.style={rectangle, minimum width=3.5cm, minimum height=1cm, text centered, draw=black, fill=gray!20},
        arrow/.style={thick,->,>=stealth}
    ]
        
        % 1. Place the Nodes (Shapes)
        \node (start) [startstop] {Paper / PDF};
        \node (proc1) [process, right=of start, xshift=-1.5cm] {Entity \& Relation Extraction};
        \node (proc2) [process, right=of proc1, xshift=-1.5cm] {PeptideMiner JSON};
        \node (proc3) [process, below=of start] {Design-Rule Cards};
        \node (proc4) [process, below=of proc2] {Phase};
        \node (stop) [startstop, left=of proc4, yshift=1cm] {Science Skill};
        
        % 2. Draw the Arrows (Connections)
        \draw [arrow] (start) -- (proc1);
        \draw [arrow] (proc1) -- (proc2);
        
        % Split path from Experiment to Peptide
        \draw [arrow] (proc1) -- (proc3);
        
        % Converging paths to Phase
        \draw [arrow] (proc2) -- (proc4);
        \draw [arrow] (proc3) -- (proc4);
        
        \draw [arrow] (proc4) -- (stop);
        
    \end{tikzpicture}
    \caption{Instantiated Graph Schema.}
    \label{fig:scope}
\end{figure}

\begin{remark}
  With the recent release of GPT-5.6 Sol, which is optimized for PDF knowledge extraction graph schema conversion, we proposed a new pipeline that ingests unmodified .pdf documents using frontier models. This bypasses intermediate .md conversions, which preserves figure order and captions.  
\end{remark}

\subsection{Agentic Architecture}
The extraction process executed through a multi-agent framework as opposed to a single off-the-shelf LLM. The following specialized agents were used: 
\begin{itemize}
    \item Section Agent
    \begin{itemize}
        \item Isolates relevant sections
    \end{itemize}
    \item Entity and Relation Agents
    \begin{itemize}
        \item Extracts and relates target entities that correspond with the 13-feature schema
    \end{itemize}
    \item Graph Agent
    \begin{itemize}
        \item Structures extracted entities into a formal knowledge graph
    \end{itemize}
    \item Table and Verifier Agent
    \begin{itemize}
        \item Cross-verifies the structured output to minimize hallucinations and format data
    \end{itemize}
    \item Classifier Agent
    \begin{itemize}
        \item Finalizes morphology classification in predefined classes.
    \end{itemize}
\end{itemize}

\subsection{Graph Schema}
The Graph Agent mapped extracted data to a structured knowledge graph based on a core relation: peptide $+$ experimental condition $\rightarrow$ phase.

\begin{figure}[htb]
    \centering
    \begin{tikzpicture}[
        node distance=2cm, auto,
        startstop/.style={rectangle, rounded corners, minimum width=3.5cm, minimum height=1cm, text centered, draw=black, fill=purple!20},
        process/.style={rectangle, minimum width=3.5cm, minimum height=1cm, text centered, draw=black, fill=gray!20},
        arrow/.style={thick,->,>=stealth}
    ]
        
        % 1. Place the Nodes (Shapes)
        \node (start) [startstop] {Paper};
        \node (proc1) [process, right=of start] {Experiment};
        \node (proc2) [process, right=of proc1] {Condition};
        \node (proc3) [process, below=of proc1, yshift=1.25cm] {Peptide};
        \node (proc4) [process, below=of proc2] {Phase};
        \node (stop) [startstop, left=of proc4, xshift = -4cm] {Evidence};
        
        % 2. Draw the Arrows (Connections)
        \draw [arrow] (start) -- (proc1);
        \draw [arrow] (proc1) -- (proc2);
        
        % Split path from Experiment to Peptide
        \draw [arrow] (proc1) -- (proc3);
        
        % Converging paths to Phase
        \draw [arrow] (proc2) -- (proc4);
        \draw [arrow] (proc3) -- (proc4);
        
        \draw [arrow] (proc4) -- (stop);
        
    \end{tikzpicture}
    \caption{Instantiated Graph Schema.}
    \label{fig:schema}
\end{figure}

This formal graph schema resolved issues caused by multiple experiments on the same peptide within the same paper, which was a primary source of error non-graph-based LLM extractions. 

\subsection{Validation Protocol}
The graph agent workflow performance was evaluated against the 75 paper datasets and were also used to train Random Forest (RF) and Multi-Layer Perceptron (MLP) algorithms to verify the workflow enhances phase prediction accuracy.

\section{Acknowledgements}
I would like to thank Professor Markus J. Buehler and Dr. Subhadeep Pal at the Laboratory for Atomistic and Molecular Mechanics for their invaluable help. I would also like to thank the Research Science Institute, the Center for Excellence in Education, and the Massachusetts Institute of Technology for this amazing opportunity.